---
title: "Biologist Role"
author: "Simran"
date: "4/8/2020"
output: word_document
---

Filter deseq results based on abs(log2foldchange > 1 and pval < 0.05)
```{r echo = FALSE, message = FALSE}

filter_deseq <- function(filename) {
  data <- read.csv(paste0("analysis/deseq_files/", filename))
  data <- data[data$padj < 0.05,]
  data <- data[abs(data$log2FoldChange) > 1,]
  data <- data[!is.na(data$X),]
  write.csv(data, paste0("analysis/deseq_files/filtered_", filename))
}

filter_deseq("deseq_mode1.csv")
filter_deseq("deseq_mode2.csv")
filter_deseq("deseq_mode3.csv")



# try taking top 500 in each log2fold change direction
# use gsea preranked
# give a list of genes and fold changes

```



```{r echo = FALSE, message = FALSE}
#install.packages("gplots")
library(gplots)

norm1 <- read.csv("analysis/norm_counts/deseq_norm_counts_mode1.csv")
rownames(norm1) <- norm1$X
norm1 <- norm1[-1]
heatmap(as.matrix(norm1))

norm2 <- read.csv("analysis/norm_counts/deseq_norm_counts_mode2.csv")
rownames(norm2) <- norm2$X
norm2 <- norm2[-1]
heatmap(as.matrix(norm2))

norm3 <- read.csv("analysis/norm_counts/deseq_norm_counts_mode3.csv")
rownames(norm3) <- norm3$X
norm3 <- norm3[-1]
heatmap(as.matrix(norm3))

combined <- cbind(norm1, norm2, norm3)

cols <- which(names(combined) == 'SRR1178030')
names(combined)[cols] <- paste0('SRR1178030_', seq_along(cols))

cols <- which(names(combined) == 'SRR1178040')
names(combined)[cols] <- paste0('SRR1178040_', seq_along(cols))

cols <- which(names(combined) == 'SRR1178056')
names(combined)[cols] <- paste0('SRR1178056_', seq_along(cols))

data <- data.frame(".3_METHYLCHOLANTHRENE_1" = combined$SRR1177997,
                   ".3_METHYLCHOLANTHRENE_2" = combined$SRR1177999,
                   ".3_METHYLCHOLANTHRENE_3" = combined$SRR1178002,
                   "FLUCONAZOLE_1" = combined$SRR1178014,
                   "FLUCONAZOLE_2" = combined$SRR1178021,
                   "FLUCONAZOLE_3" = combined$SRR1178047,
                   "PIRINIXIC_ACID_1" = combined$SRR1177963,
                   "PIRINIXIC_ACID_2" = combined$SRR1178064,
                   "PIRINIXIC_ACID_3" = combined$SRR1177965,
                   "CONTROL_CMC_1" =  mean(cbind(combined$SRR1178030_1, combined$SRR1178030_2)),
                   "CONTROL_CMC_2" = mean(cbind(combined$SRR1178040_1, combined$SRR1178040_2)),
                   "CONTROL_CMC_3" = mean(cbind(combined$SRR1178056_1, combined$SRR1178056_2))
)

heatmap(t(data), keep.dendro = FALSE, Rowv = NA, scale = 'col')

```



```{r echo = FALSE, message = FALSE}
library(knitr)
library(scales)

split_name <- function(str) {
  res <- strsplit(as.character(str), ':')
  res <- res[[1]][2]
  return(res)
}

make_pretty_table <- function(path_file) {
  path <- read.csv(paste0("analysis/deseq_files/", path_file), sep = '\t')
  path <- path[order(path$FDR),]
  path <- path[path$FDR < 0.05,]
  path$Pathway <- lapply(path$Term, split_name)
  path$'P-Val' <- lapply(path$PValue, scientific)
  path$FDR <- lapply(path$FDR, scientific)
  return(path[,c(14, 15, 13)])
}


kable(make_pretty_table("pathways_mode1.csv"))
kable(make_pretty_table("pathways_mode2.csv"))
kable(make_pretty_table("pathways_mode3.csv"))


```





